Assessing exposure to Atlantic Basin tropical storms in United States counties

### 2016-07-28 writing/DraftExposurePaper/DraftExposurePaper.Rmd
ike reporting stations code

```{r}
my_fips <- ike_fips[c(1:6, 10, 13:16, 18, 20:25, 28:29, 31, 33:34, 36:40, 42, 44:45)]
my_stations <- NA
ike_table <- expand.grid(my_fips, my_stations)
colnames(ike_table) <- c("fips", "station")
for(fips in my_fips){
        ike_weather <- weather_fips(fips = fips,
                                    date_min = "2008-09-01",
                                    date_max = "2008-09-14",
                                    var = "PRCP")
        ike_table[ike_table$fips == fips, "station"] <- max(ike_weather$daily_weather$prcp_reporting)    
} #This works fine (small subset of the code below)
my_fips <- ike_fips[44:45]
my_stations <- NA
test_2 <- expand.grid(my_fips, my_stations)
colnames(test_2) <- c("fips", "station")
for(fips in my_fips){
        ike_weather <- weather_fips(fips = fips,
                                    date_min = "2008-09-01",
                                    date_max = "2008-09-14",
                                    var = "PRCP")
        test_2[test_2$fips == fips, "station"] <- max(ike_weather$daily_weather$prcp_reporting)    
}
#Do not work: 7, 8, 9, 11, 12, 17, 19, 26, 27, 30, 32,35, 41, 43, 
ike_table <- ike_table %>%
        arrange(desc(station)) %>%
        slice(1:15)
ike_table <- expand.grid(ike_fips, my_stations)
colnames(ike_table) <- c("fips", "station")
#for(fips in ike_fips){
        ike_weather <- weather_fips(fips = fips,
                                    date_min = "2008-09-01",
                                    date_max = "2008-09-14",
                                    var = "PRCP")
        ike_table[ike_table$fips == fips, "station"] <- max(ike_weather$daily_weather$prcp_reporting)
} #getting error
```

>>>>

```{r}
#Find the top 15 FIPS by number of reporting stations during Ike-2008
my_fips <- ike_fips[c(1:6, 10, 13:16, 18, 20:25, 28:29, 31, 33:34, 36:40, 42, 44:45)]
my_stations <- NA
ike_table <- expand.grid(my_fips, my_stations)
colnames(ike_table) <- c("fips", "station")
for(fips in my_fips){
        ike_weather <- weather_fips(fips = fips,
                                    date_min = "2008-09-01",
                                    date_max = "2008-09-14",
                                    var = "PRCP")
        ike_table[ike_table$fips == fips, "station"] <- max(ike_weather$daily_weather$prcp_reporting)    
} 
#Do not work: 7, 8, 9, 11, 12, 17, 19, 26, 27, 30, 32,35, 41, 43, 
ike_table <- ike_table %>%
        arrange(desc(station)) %>%
        slice(1:15)
```
